---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
    citation_package: biblatex
  bookdown::html_document2: default
  bookdown::word_document2: default
documentclass: book
#bibliography: [bibliography/references.bib, bibliography/additional-references.bib]
---


```{=tex}
\adjustmtc
\markboth{Methods}{}
```


# Results and Discussion {#discussion}


<!-- Data are reported as figures in Appendix \@ref(a-figures) and tables in Appendix \@ref(a-tables). Data are organized by result e.g. Volume, and then listed per ligand.  -->

<!-- <!-- # Discussion {#discussion} --> -->

<!-- This section is organized by type of result; figures and tables referenced are within the appendices. -->

## Analysis of Nearby Residues of Natural Porphyrins

The first part of the study aimed at providing statistics on the amino acid propensity to interact with hemes in natural proteins. We studied heme-b, heme-c, siroheme and verdoheme. Because we are not looking only at the iron environment, but instead at the  environment of the entire microcycle, we did the analysis for any amino acid with potential contact with the heme. This was defined as any AA having at least one atom within the cutoff distances of 5 and 7 Angtroms (A). 

Amino acid frequencies were obtained for distance cutoffs of 5A and 7A - these figures and data are shown in **FIXME ADD APPENDICES LATER** The trends in these data are very similar and therefore only the data pertaining to the 7A distance cutoff are discussed below.


## AA Frequency {#disc-aaFreq}


### Heme-b

#### Amino Acid Frequencies in Binding Pocket

Figure \@ref(fig:HEM-AAfreq) plots the frequency of each residue within 7A of heme-b. Immediately below is Figure \@ref(fig:HEM-AAfreqAll), which plots the frequency of each residue within the entire monomer. **I'm thinking put tables in back they dont add much value here** Data tables are available in Appendix...

<!-- Actually lets do the pocket first. They're not super duper similar after all.  -->
**We gotta fuck ton of shit to discuss! Don't try to keep this short homie. You've put in WORK.**

Beginning at the left of the figure and moving right, large, nonpolar amino acids appear most frequently within 7A: LEU and PHE; ILE appears less frequently than these two amino acids but nonetheless is in high frequency. Small, nonpolar amino acids ALA and VAL also appear very frequently. As the majority of the heme-b molecule is made up of the nonpolar porphyrin ring, these amino acids are therefore likely in such high frequency to provide the nonpolar interactions/environment with the pyrole groups and methyl and vinyl groups. 

**Note hisitidine is highly evolutionarily conserved to coordinate Fe, and it may be affected by the molecules we've chosen based on what they used to coordinate - I don't want to examine that right now though so moving on**
Tyrosine, arginine, histidine appear next most frequently. The two propionate groups on heme are used to coordinate the heme in the binding pocket. These polar residues are therefore likely interact with the propionate groups, providing the polar interactions necessary, in addition to the nonpolar interactions above, to provide as hospitable of a binding environment as possible to coordinate the heme. In additon, the arginine and histidine groups are positively charged (at pH 7), **further facilitating interaction with the electronegative proprionate groups on the porphyrin ring of heme-b.** GOTTA FACT CHECK THIS HOMIE-YO.

Glycine is a small residue and cannot form significant interactions within its environment; however, its frequency, or lack thereof (compared to background frequency, discused later), suggests the binding pocket may not require as much flexibility or... spatial considerations as in the rest of the protein. This would logically follow from the need for conserved binding sites.

Serine glu asp*
Next appear serine, glutamate (glutamic acid) and aspartate (aspartic acid) and lysine. These are polar residues, and glutamate and aspartate are negatively charged; lysine is polarpositively charged. The negative charge is unlikely of importance in interaction with heme-b, however these polar amino acids likely again interact with the propionate groups on heme; only, infrequently. What is most interesting is why lysine is in such low abundance relative to the other polar, positively charged residues, arginine and histidine. Perhaps lysine's fairly linear structure prevents it from fitting into the binding pocket; however, arginine is also somewhat linear and features prominently. The exact reason for why this could be is beyond the scope of this study.  

Proline is a small nonpolar amino acid in low frequency; the trend for heme-b, at least, appears to be to favor large nonpolar amino acids in the binding pocket. This may suggest that a large amount of nonpolar interactions, per residue, is favored in the binding pocket, perhaps because of the limited space available to position residues to interact with heme.

Asparagine and glutamine are both medium-sized polar amino acids; given the trends already discussed it is surprising these are not in greater abundance. But as with proline, it may simply be a matter of maximizing the benefit of the interactions that may be formed with the heme; while asparagine and glutamine are polar, amino acids like arginine and histidine are both polar and positively charged, capable of stronger interactions with the electronegative propionate groups.

met, trp
Methionine and tryptophan appear very infrequently in the binding pocket. All nonpolar amino acids already mentioned do not possess a sulfur (thio something?) bond in their structure; perhaps it is less favorable for the sulfur atom to interact with the porphyrin ring than another carbon. Tryptophan is very surprising to find as second-to-least frequent. It is a large nonpolar amino acid - but perhaps its single, potential hydrogen bond, although weak, is enough to prefer completely nonpolar residues. Or, with its size, it is preferable to have more numerous, smaller nonpolar residues that can favorably interact with the porphyrin while taking up less space.

Cystine appears most infrequently of all the amino acids in the binding pocket. This is quite  surprising - cystine is highly evolutionarily conserved to coordinate the iron in the binding pocket. Perhaps the sample of PDBs used in this study mostly use histidine to coordinate the iron - but this would only account for one residue in the binding pocket. Therefore these results suggest that while cystidine may be well suited to coordinate the iron in heme, it is poorly suited to form any nonpolar interactions with the porphyrin ring, leaving the task up to other, more suitably/intensely nonpolar amino acids.
**also need to talk about this with his**

Moving away from discussing individual amino acid populations, what is especially notable of the data for heme-b is that nonpolar residues appear in much greater frequency than polar residues. Nonpolar interactions with heme are therefore more numerous than polar interactions; quite logical, given there are only two polar propionate groups on a large porphyrin ring that is otherwise nonpolar. Their multiplicity may also suggest that they are potentially of greater importance than previously thought. At the very least, these results suggest that polar interactions and coordination of the iron atom, while necessary for heme binding, are insufficient, and that nonpolar intercations and the population of nopolar residues in the binding pocket should be considered when examining the binding environment of heme.

```{r HEM-AAfreq,fig.cap="HEM: AA Frequency within 7A",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

#### Comparison with Background Amino Acid Frequencies

While the frequencies of amino acids in the binding pocket have been discussed, it may also be of interest to compare against the background amino acid frequency, the general frequency of amino acids within the entire monomer. The degree to which this may affect the significance of the frequencies of the amino acids in the binding pocket is unclear - those amino acids are still employed and placed such as to bind the heme, rather than being a random assortment of residues. However, a in depth examination of simlarities and differences may reveal that some amino acids may simply be extremely highly conserved by chance and by virtue of their numerous population, rather than some chemical benefit.

Figure \@ref(HEM-AAfreqAll) documents the frequencies of amino acids overall within the monomer.

Leucine and alanine as in the binding pocket frequencies are highly frequent in the overall monomer. This may suggest their prevalence in the binding pocket may simply be due to a high pulation of leucine and alanine in hemoproteins.

However, after these two amino acids the tendencies in frequency for the binding pocket and the monomer at large diverge. 

Glycine is in high frequency - likely due to more complex geometry e.g. helices outside the binding pocket. In interest of brevity, the remaining frequencies are summed up thus: the same trends that appear to exist in the binding pocket do not appear to exist in the monomer at large. While the order of frequencies in conserved binding pockets can be rationalized, justifying the overall frequencies in monomers invites significant speculation. 

```{r HEM-AAfreqAll,fig.cap="HEM: AA Frequency of Monomer",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqAllDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=0.65) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency of Monomer",sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r HEM-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```


#### Distributon of Amino Acids over Distance

After an exhaustive exploration of the relative frequencies of amino acids in the binding pocket, the figure below likely appears fairly straightfoward. Figure \@ref(HEM-AAdist) plots the distribution of amino acids in the binding pocket against their distance from the iron of the heme. 

We find that only a few residues come in close contact (<4A) of the heme: Cys, His, Tyr. Most residues center their distribution at around 6A, although Lys seems more biased than the remaining residues to be a bit closer. Cystidine and histidine may be at least in part explained to be close due to their use as coordnating residues; histidine, being in greater frequency, may also be this close due to favorable interactions with the porphyrin ring. 

The proximity of tyrosine  however, is lkely more notable. It cannot form coordination bonds with the heme iron, but tyrosine residues do interact with the propionate groups; and these results suggest that of all potentially interacting polar/positively charged residues, tyrosine is the most likely at least to be in close proximity to the heme molecule. Whether this illustrates an extreme imortance of tyrosine to interact with propionate groups, or instead the need for tyrosine to be in close proximity in order to form such interactions, is beyond the scope of this study. 

```{r HEM-AAdist,fig.cap="HEM: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

### Heme-c

Leucine and alanine again are highly frequent for HEC, followed by quite similar trends and therfore HEC will not be as thoroughly discussed as HEM. The most notable differences may be that GLY and CYS are in far higher frequency than in heme. Heme-c almost always covalently binds to CYS, and this may explain that frequency: but as for glycine, perhaps the covalent binding of CYS is sufficient for other interactions to be of lower priority, and the flexibility and shape of the binding pocket to be prioritized, therefore leading to more glycines being included in order to shape the pocket favorably. **I feel like this is grasping at straws without much support, add more qualifiers or just leave it at not discussing much**

```{r HEC-AAfreq,fig.cap="HEC: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r HEC-AAfreqAll,fig.cap="HEC: AA Frequency of Monomer",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqAllDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=0.65) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency of Monomer",sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

Generally, heme-c mirrors heme-b in a strong showing of alanine and leucine, followed by a divergence in the frequency of amino acids and therefore a struggle to form any meaningful discussion when it comes to comparing the binding pocket frequencies against background frequencies.  

```{r HEC-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r HEC-AAdist,fig.cap="HEC: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

The distribution of amino acids over distance from the heme iron for HEC is similar to HEM, with some exceptions. Cys, His, Tyr again are amongst the closest residues to HEC, likely for the same reasons of very strong polar interactions or coordination. Additionally, cysteine covalently bonds to HEC's iron atom, providing further justification for its proximity. However, for HEC, Lys and Met also are very proximal. The methionine residues... for thioester bonds?? **HELP** Lysine is polar and positively charged, and therefore in the case of HEC being covalently bonded, and therefore reliably, specifically, positioned, the environment may be such that a lengthy, polar, charged residue may also be positioned well enough to be consistently nearby and forming interactions with the propionate groups.
**review this one home dawg**


### Verdoheme

Verdoheme is dissimilar from HEM and HEC above. This is fairly surprising, given that verdoheme is an intermediate in the binding pocket for heme within heme oxygenases. The results discussed below may be attributable to the small sample size of verdoheme PDBs (n=4, combining VEA and VER), and should be appreciated with some skepticism. Nonetheless, the results will be discussed.

Leucine and alanine are again most frequent, but after this results diverge. Tyrosine is next most frequent - surprising, given that this is still the same pocket that bound heme. It is possible that heme's reorientation during its degradation moves it closer to another region of the binding pocket. Chemically, it may be that as heme is oxidized, there is greater need to  and arginine are next most frequent;  **looking ahead, the residue by distance looks baaaaad. So gonna hold off on discussing this until after siroheme. But, do finish the amino acid discussion, after this we're in the home stretch lol**

```{r VERDOHEME-AAfreq,fig.cap="VERDOHEME: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r VERDOHEME-AAfreqAll,fig.cap="VERDOHEME: AA Frequency of Monomer",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqAllDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=0.65) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency of Monomer",sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```


```{r VERDOHEME-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r VERDOHEME-AAdist,fig.cap="VERDOHEME: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

### Siroheme

Siroheme, with a structure highly dissimilar to the other heme molecules examined, should be expected to have a different amino acid frequency profile - and indeed we confirm this in our results. 

Rather than nonpolar residues being most abundant, disproportionately frequent to the rest of the residues in the binding pocket is arginine. Siroheme is saturated with carboxyl and propionate groups, the entire porphyrin ring surrounded by polar, electronegative groups. 
```{r SRM-AAfreq,fig.cap="SRM: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r SRM-AAfreqAll,fig.cap="SRM: AA Frequency of Monomer",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqAllDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=0.65) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency of Monomer",sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```


```{r SRM-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r SRM-AAdist,fig.cap="SRM: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```




<!-- For the sake of this report, both sets of data are overlaid in the same figures in (section). However, the general tendencies are very similar and only the 7A data will be discussed. -->


<!-- Amino acid frequencies within the 5A and 7A distance cutoffs of the ligand are reported in Appendix \@ref(figs-aaFreq) and **(FIXME! Missing amino acid tables)** -->

<!-- ### Heme-b and Heme-c -->
### Heme-c



<!-- The top 5 residues for HEM and HEC both include leucine, phenylalanine, alanine, and isoleucine; valine and glycine are the other for each ligand respectively. -->
<!-- Do not over generalize, but discuss mucho -->

Interacts with the propionates, the polar groups within the porphyrin - 
1.    


Thus, we confirm with (@Li2011) that the binding site for heme-b, and now additionally heme-c, is enriched with nonpolar amino acids. This strongly suggests that the nonpolar amino acids are crucial to the binding of heme, likely due to the favorable interaction between the nonpolar amino acids and the porphyrin ring of heme-b and heme-c. The degree to which the percentage of nonpolar acids in the binding pocket may affect the binding of heme cannot be determined in this analysis. But the agreement with the residues closest to heme (and therefore likely to coordinate) is discussed below.
<!-- FIXME: DO FUCKING DISCUSS IT -->
### Siroheme

The binding pocket for siroheme is highly enriched with arginine, in addition to other charged residues such as lysine and cysteine. Given  the function of siroheme is to transfer multiple electrons per reaction, the enrichment of the binding environment with charged residues is perhaps not surprising. Addtionally, for siroheme in particular, the geometry, the placement of these residues in order to coordinate the movement of electrons may be of interest; however this is beyond the scope of this study.  

### Verdoheme

Verdoheme is an intermediate formed within the binding pocket of heme oxygenase during the degradation of heme; this is the same environment that binds heme at the beginning of the reaction. Verdoheme is oriented differently in the pocket, however overall the amino acid composition of the pocket should be quite similar if not the same. But this is not reflected in our results. Rather, relative to the amino acid... profile (?) of heme-b and heme-c, arginine is in greater abundance in the binding pocket. Leucine, alanine and phenylalanine are still amongst the most frequent amino acids, again providing nonpolar interactions. 

These results may suggest that verdoheme is reoriented, and potentially spatially relocated, to interact with more arginine residues than would be possible if the original heme orientation were maintained; the amount of space verdoheme would have to move within the binding pocket is discussed below. However, it is also possible, likely, this is an artefact of  the very small sample size of verdoheme PDBs used in this study (n=4). Upon the availability of additional verdoheme-containing PDBs in the future this result may be reexamined.


## Volume Discussion

Figures can be found in Appendix \@ref(figs-vol)..

Besides HEM, much of the volume data for the different ligands did not closely agree between different distance cutoffs. The degree to which the  method used to determine the volume of the binding pocket, Surfnet as implemented in UCSF Chimera, is affected by the distance cutoff is therefore demonstrated to be quite great. Most of the data did however fall within reasonable bounds, regardless of distance cutoffs. 

Data for heme-b, heme-c and siroheme somewhat agree within a tight range of volumes, with heme-b in particular showing the best agreement of data at approximately 800-1200A³. However, the *range* of the volume data, for all ligands, is considerable, approximately 1000A³. 

There are then at two conflicting conclusions from these data.

The the volumes of the binding pocket, as determined by calculation, are shown to not require uniform size. This suggests that the binding pocket need not be a perfect fit for each protein's respective ligand. As far as implications for protein engineering, these results suggest that de novo design of a hemoprotein may not require significant work as far as sizing of a binding pocket.

Alternatively, the results demonstrate the difficulty of calculating molecular volumes, and how error-prone at least this method may be. Comparison with other methods of calculating molecular volumes, or with experimental data, would be warranted in future study.

**also need to highlight differences in excluded v. accessible**
## Surface Area of Ligands
<!-- just combine 'em lol discussion will be the same -->
Figures can be found in Appendix \@ref(figs-ligExcSA) for ligands' solvent excluded surface area, and 
 in Appendix \@ref(figs-ligAccSA) for ligands' solvent accessible surface area. 


This measure, and also the solvent accessible surface area of the ligands, is effectively of the surface area of each ligand itself - distance cutoffs and binding environments are not expected to affect the results. Significant variability in the data may therefore suggest problems in calculation.

Both accessible and excluded surface area data are fairly well centered around some value for all ligands, except for verdoheme. For the latter this may be attributed to the small sample size. But for other ligands, and also for verdoheme, the outliers in the data may suggest errors in calculation and potential inclusion of parts of the binding pocket itself in calculation.


## Pocket Solvent Excluded Surface Area

**We'll do same treatment for pocket surface areas, skipping ahead to angles/distances**

Figures can be found in \@ref(figs-pocketExcSA)

<!-- HEM data has poor agreement for this measure. Data is concentrated from 5000-15000 A², but this is a very large range and not very useful. -->

<!-- HEC agrees in a somewhat tighter range: most data fall within 5000-7500 A²; still not very useful but better than HEM. -->

<!-- Most SRM data fall within 21000-22000 A².  -->

<!-- Verdoheme data range from 9200 to 10000 A².  -->

<!-- For this measure, then, we find that SRM and Verdoheme have a fairly specific range of predicted solvent excluded surface area for their binding pockets. -->

<!-- ## Pocket Solvent Accessible Surface Area -->

Figures can be found in Appendix \@ref(figs-pocketAccSA).

<!-- The results for this measure follow the trends for the previous section. -->

<!-- Most HEM data fall from 5000-15000 A². HEC data mostly fall from 5000-7500 A². -->

<!-- SRM data is highly concentrated at approximately 21000 A², more specific than the pocket solvent excluded surface area.  -->

<!-- Verdoheme data range from 10000-11000 A². -->

## All Planar Angles

Figures can be found in \@ref(figs-planarAll)

These data, for all ligands, except potentially for heme-c, largely serve to compare as noise for the next section. The planar angles of all residues, falling within the upper distance cutoff of 7A, are plotted. 

In the notable exception of heme-c  (HEC), Figure **FIXME: insert figure name** for this ligand seems to suggest that GLU, MET and LYS have fairly specific planar angles with the ligand. However, heme-c is not coordinated to achieve its chemistry but rather covalently bound, to histidine. Lysine is effectively the median of amino acid frequency for heme-c, methionine is even less frequent and glutamine is the least frequent amino acid. For the latter two amino acids their tight range of planar angles is therefore likely an artefact of a small sample size of amino acids. However, for lysine the tight range of angles may be significant; this is dicussed further below. 

## Planar Angles of Closest Residues

Figures can be found in \@ref(figs-planarClosest)

<!-- Here, the three closest residues to the ligand in each PDDB and their planar angle to the ligand are plotted. -->

<!-- HEM has a fairly inconclusive set of data for this measure. GLU and GLN nearby HEM do appear to fall within a tight range, though, of approximately 75 degrees and 80 degrees respectively. -->

<!-- The data for residues nearby HEC diverge from what is found for all residues around HEC. The most agreement is found for ILE and LYS, with angles concentrated about 50 degrees and 75 degrees, respectively. -->

<!-- Only three types of residues appear nearby SRM: CYS, LYS, and ARG. Although their angles vary wildly, these data suggest these residues are important to the coordination fo SRM. (FIXME! Add reasoning) -->

<!-- Verdoheme also has a small selection of residues that are close to the ligand. GLY and HIS are the only residues that are close to the ligand in the PDBs used in this study. (FIXME! Add reasoning... or qualifier statement n=2) -->

## All CA-CB-Fe Angles

Figures can be found in \@ref(figs-cabAll)

<!-- All residues have a broad range of angles in relation to HEM. -->

<!-- Most residues have a broad range of angles for HEC, with the exception of THR, which has a tight distribution around 100 degrees. This result only appears here and does not follow for the closest residues, and therefore may be due to a small sample size of THR residues. -->

<!-- SRM appears to have tight distributions of angles when considering all residues; the residues closest to SRM do not echo this. Although likely attributable to a small sample size, there appear several residues with specific angles: ALA around 50 degrees, GLN around 140-150 degrees, and SER around 50 degrees. -->

<!-- Verdoheme... (FIXME! Confer with JeanDi before we report more of these angles. Not sure I'm going about it in an informative way. Also add figure numbers.) -->

## CA-CB-Fe Angles of Closest Residues

Figures can be found in \@ref(figs-cabClosest)

Most notably, HIS is the only residue that appears near verdoheme.

## Limitations of the Study
Limited sample size

Limited experimental data to reference to verify

NO experimental data in this study to verify, all theoretical

Only one software package/few algorithms used to calculate all these properties. Others were evaluated but none are compared w.

Algorithms may introduce bias based on how they work e.g. all the bubbles

Arbitrary selection of parameters; some based on rule of thumb or visual evaluation but all or almost all arbitrary

Unknown if the qualities measured are truly the most critical for the heme binding. Some papers suggest other properties may also be important but cannot be calculated, at least right now, e.g. ionic bonding strength etc.

Visual examination itself to OK the parameters/algorithms can introduce bias