---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
    citation_package: biblatex
  bookdown::html_document2: default
  bookdown::word_document2: default
documentclass: book
#bibliography: [bibliography/references.bib, bibliography/additional-references.bib]
---


```{=tex}
\adjustmtc
\markboth{Methods}{}
```


# Results and Discussion {#discussion}


<!-- Data are reported as figures in Appendix \@ref(a-figures) and tables in Appendix \@ref(a-tables). Data are organized by result e.g. Volume, and then listed per ligand.  -->

<!-- <!-- # Discussion {#discussion} --> -->

<!-- This section is organized by type of result; figures and tables referenced are within the appendices. -->

## Analysis of Nearby Residues of Natural Porphyrins

The first part of the study aimed at providing statistics on the amino acid propensity to interact with hemes in natural proteins. We studied heme-b, heme-c, siroheme and verdoheme. Because we are not looking only at the iron environment, but instead at the  environment of the entire microcycle, we did the analysis for any amino acid with potential contact with the heme. This was defined as any AA having at least one atom within the cutoff distances of 5 and 7 Angtroms (A). 

Amino acid frequencies were obtained for distance cutoffs of 5A and 7A - these figures and data are shown in **FIXME ADD APPENDICES LATER** The trends in these data are very similar and therefore only the data pertaining to the 7A distance cutoff are discussed below.


## AA Frequency {#disc-aaFreq}


### Heme-b

Figure \@ref(fig:HEM-AAfreq) plots the frequency of each residue within 7A of heme-b. Immediately below is Figure \@ref(fig:HEM-AAfreqAll), which plots the frequency of each residue within the entire monomer. **I'm thinking put tables in back they dont add much value here** Data tables are available in Appendix...

<!-- Actually lets do the pocket first. They're not super duper similar after all.  -->
**We gotta fuck ton of shit to discuss! Don't try to keep this short homie. You've put in WORK.**

Beginning at the left of the figure and moving right, large, nonpolar amino acids appear most frequently within 7A: LEU and PHE; ILE appears less frequently than these two amino acids but nonetheless is in high frequency. Small, nonpolar amino acids ALA and VAL also appear very frequently. As the majority of the heme-b molecule is made up of the nonpolar porphyrin ring, these amino acids are therefore likely in such high frequency to provide the nonpolar interactions/environment with the pyrole groups and methyl and vinyl groups. 

Tyrosine, arginine, histidine appear next most frequently. The two propionate groups on heme are used to coordinate the heme in the binding pocket. These polar residues are therefore likely interact with the propionate groups, providing the polar interactions necessary, in addition to the nonpolar interactions above, to provide as hospitable of a binding environment as possible to coordinate the heme. In additon, the arginine and histidine groups are positively charged (at pH 7), **further facilitating interaction with the electronegative proprionate groups on the porphyrin ring of heme-b.** GOTTA FACT CHECK THIS HOMIE-YO.

Glycine is a small residue and cannot form significant interactions within its environment; however, its frequency, or lack thereof (compared to background frequency, discused later), suggests the binding pocket may not require as much flexibility or... spatial considerations as in the rest of the protein. This would logically follow from the need for conserved binding sites.

ser, glu, asp, lys, pro, asn, gln, met, trp, cys

Serine glu asp*
Next appear serine, glutamate (glutamic acid) and aspartate (aspartic acid) and lysine. These are polar residues, and glutamate and aspartate are negatively charged; lysine is polarpositively charged. The negative charge is unlikely of importance in interaction with heme-b, however these polar amino acids likely again interact with the propionate groups on heme; only, infrequently. What is most interesting is why lysine is in such low abundance relative to the other polar, positively charged residues, arginine and histidine. Perhaps lysine's fairly linear structure prevents it from fitting into the binding pocket; however, arginine is also somewhat linear and features prominently. The exact reason for why this could be is beyond the scope of this study.  

proline are nonpolar 

asn gln

met, trp

cys

What is especially notable is that nonpolar residues appear in much greater frequency than polar residues. This suggests that the nonpolar interactions with heme may be of greater importance than the coordination of polar residues in the binding pocket; at the least, more important than previously thought.  


It is immediately striking that some amino acids, e.g. LEU and ALA, are among the most populous amino acids for both the binding pocket and in the entire monomer.


```{r HEM-AAfreq,fig.cap="HEM: AA Frequency within 7A",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

after the aa freq in the pocket!! 

```{r HEM-AAfreqAll,fig.cap="HEM: AA Frequency of Monomer",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqAllDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=0.65) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency of Monomer",sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

now we be after the aa freq of monomer and about to go into the awesome table yay

```{r HEM-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```




```{r HEM-AAdist,fig.cap="HEM: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

### Heme-c

```{r HEC-AAfreq,fig.cap="HEC: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r HEC-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r HEC-AAdist,fig.cap="HEC: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

### Verdoheme

```{r VERDOHEME-AAfreq,fig.cap="VERDOHEME: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r VERDOHEME-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r VERDOHEME-AAdist,fig.cap="VERDOHEME: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```

### Siroheme
```{r SRM-AAfreq,fig.cap="SRM: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

print(ggplot(eval(parse(text=paste(activeLigand,"_aaFreqDf",sep=""))),aes(x= reorder(Residue,-Freq),y=Freq))  +
      geom_bar(stat="identity",position = "identity", alpha=1) +
      labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency within 7A of ",activeLigand,sep='')) +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

```

```{r SRM-t-AAfreq,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_aaFreqDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM AA Freq") %>%
  kable_styling(latex_options = c("striped","repeat_header"))

```

```{r SRM-AAdist,fig.cap="SRM: AA Distances",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

eval(parse(text=paste(activeLigand,"_distList$mean_distances",sep=""))) %>%
      dplyr::select(Residue_Code,Mean_Distance) -> tmpDist 
   
   distanceDist <- ggplot(tmpDist,aes(x=Residue_Code,y=(as.numeric(as.character(Mean_Distance))),fill=Residue_Code)) + 
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": Distribution of Residues by Mean_Distance",sep=''), x="Residue",y="Mean_Distance (Å)") +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

   print(distanceDist)
   
```




<!-- For the sake of this report, both sets of data are overlaid in the same figures in (section). However, the general tendencies are very similar and only the 7A data will be discussed. -->


<!-- Amino acid frequencies within the 5A and 7A distance cutoffs of the ligand are reported in Appendix \@ref(figs-aaFreq) and **(FIXME! Missing amino acid tables)** -->

<!-- ### Heme-b and Heme-c -->
### Heme-c



<!-- The top 5 residues for HEM and HEC both include leucine, phenylalanine, alanine, and isoleucine; valine and glycine are the other for each ligand respectively. -->
<!-- Do not over generalize, but discuss mucho -->

Interacts with the propionates, the polar groups within the porphyrin - 
1.    


Thus, we confirm with (@Li2011) that the binding site for heme-b, and now additionally heme-c, is enriched with nonpolar amino acids. This strongly suggests that the nonpolar amino acids are crucial to the binding of heme, likely due to the favorable interaction between the nonpolar amino acids and the porphyrin ring of heme-b and heme-c. The degree to which the percentage of nonpolar acids in the binding pocket may affect the binding of heme cannot be determined in this analysis. But the agreement with the residues closest to heme (and therefore likely to coordinate) is discussed below.
<!-- FIXME: DO FUCKING DISCUSS IT -->
### Siroheme

The binding pocket for siroheme is highly enriched with arginine, in addition to other charged residues such as lysine and cysteine. Given  the function of siroheme is to transfer multiple electrons per reaction, the enrichment of the binding environment with charged residues is perhaps not surprising. Addtionally, for siroheme in particular, the geometry, the placement of these residues in order to coordinate the movement of electrons may be of interest; however this is beyond the scope of this study.  

### Verdoheme

Verdoheme is an intermediate formed within the binding pocket of heme oxygenase during the degradation of heme; this is the same environment that binds heme at the beginning of the reaction. Verdoheme is oriented differently in the pocket, however overall the amino acid composition of the pocket should be quite similar if not the same. But this is not reflected in our results. Rather, relative to the amino acid... profile (?) of heme-b and heme-c, arginine is in greater abundance in the binding pocket. Leucine, alanine and phenylalanine are still amongst the most frequent amino acids, again providing nonpolar interactions. 

These results may suggest that verdoheme is reoriented, and potentially spatially relocated, to interact with more arginine residues than would be possible if the original heme orientation were maintained; the amount of space verdoheme would have to move within the binding pocket is discussed below. However, it is also possible, likely, this is an artefact of  the very small sample size of verdoheme PDBs used in this study (n=4). Upon the availability of additional verdoheme-containing PDBs in the future this result may be reexamined.


## Volume Discussion

Figures can be found in Appendix \@ref(figs-vol)..

Besides HEM, much of the volume data for the different ligands did not closely agree between different distance cutoffs. The degree to which the  method used to determine the volume of the binding pocket, Surfnet as implemented in UCSF Chimera, is affected by the distance cutoff is therefore demonstrated to be quite great. Most of the data did however fall within reasonable bounds, regardless of distance cutoffs. 

Data for heme-b, heme-c and siroheme somewhat agree within a tight range of volumes, with heme-b in particular showing the best agreement of data at approximately 800-1200A³. However, the *range* of the volume data, for all ligands, is considerable, approximately 1000A³. 

There are then at two conflicting conclusions from these data.

The the volumes of the binding pocket, as determined by calculation, are shown to not require uniform size. This suggests that the binding pocket need not be a perfect fit for each protein's respective ligand. As far as implications for protein engineering, these results suggest that de novo design of a hemoprotein may not require significant work as far as sizing of a binding pocket.

Alternatively, the results demonstrate the difficulty of calculating molecular volumes, and how error-prone at least this method may be. Comparison with other methods of calculating molecular volumes, or with experimental data, would be warranted in future study.

**also need to highlight differences in excluded v. accessible**
## Surface Area of Ligands
<!-- just combine 'em lol discussion will be the same -->
Figures can be found in Appendix \@ref(figs-ligExcSA) for ligands' solvent excluded surface area, and 
 in Appendix \@ref(figs-ligAccSA) for ligands' solvent accessible surface area. 


This measure, and also the solvent accessible surface area of the ligands, is effectively of the surface area of each ligand itself - distance cutoffs and binding environments are not expected to affect the results. Significant variability in the data may therefore suggest problems in calculation.

Both accessible and excluded surface area data are fairly well centered around some value for all ligands, except for verdoheme. For the latter this may be attributed to the small sample size. But for other ligands, and also for verdoheme, the outliers in the data may suggest errors in calculation and potential inclusion of parts of the binding pocket itself in calculation.


## Pocket Solvent Excluded Surface Area

**We'll do same treatment for pocket surface areas, skipping ahead to angles/distances**

Figures can be found in \@ref(figs-pocketExcSA)

<!-- HEM data has poor agreement for this measure. Data is concentrated from 5000-15000 A², but this is a very large range and not very useful. -->

<!-- HEC agrees in a somewhat tighter range: most data fall within 5000-7500 A²; still not very useful but better than HEM. -->

<!-- Most SRM data fall within 21000-22000 A².  -->

<!-- Verdoheme data range from 9200 to 10000 A².  -->

<!-- For this measure, then, we find that SRM and Verdoheme have a fairly specific range of predicted solvent excluded surface area for their binding pockets. -->

<!-- ## Pocket Solvent Accessible Surface Area -->

Figures can be found in Appendix \@ref(figs-pocketAccSA).

<!-- The results for this measure follow the trends for the previous section. -->

<!-- Most HEM data fall from 5000-15000 A². HEC data mostly fall from 5000-7500 A². -->

<!-- SRM data is highly concentrated at approximately 21000 A², more specific than the pocket solvent excluded surface area.  -->

<!-- Verdoheme data range from 10000-11000 A². -->

## All Planar Angles

Figures can be found in \@ref(figs-planarAll)

These data, for all ligands, except potentially for heme-c, largely serve to compare as noise for the next section. The planar angles of all residues, falling within the upper distance cutoff of 7A, are plotted. 

In the notable exception of heme-c  (HEC), Figure **FIXME: insert figure name** for this ligand seems to suggest that GLU, MET and LYS have fairly specific planar angles with the ligand. However, heme-c is not coordinated to achieve its chemistry but rather covalently bound, to histidine. Lysine is effectively the median of amino acid frequency for heme-c, methionine is even less frequent and glutamine is the least frequent amino acid. For the latter two amino acids their tight range of planar angles is therefore likely an artefact of a small sample size of amino acids. However, for lysine the tight range of angles may be significant; this is dicussed further below. 

## Planar Angles of Closest Residues

Figures can be found in \@ref(figs-planarClosest)

<!-- Here, the three closest residues to the ligand in each PDDB and their planar angle to the ligand are plotted. -->

<!-- HEM has a fairly inconclusive set of data for this measure. GLU and GLN nearby HEM do appear to fall within a tight range, though, of approximately 75 degrees and 80 degrees respectively. -->

<!-- The data for residues nearby HEC diverge from what is found for all residues around HEC. The most agreement is found for ILE and LYS, with angles concentrated about 50 degrees and 75 degrees, respectively. -->

<!-- Only three types of residues appear nearby SRM: CYS, LYS, and ARG. Although their angles vary wildly, these data suggest these residues are important to the coordination fo SRM. (FIXME! Add reasoning) -->

<!-- Verdoheme also has a small selection of residues that are close to the ligand. GLY and HIS are the only residues that are close to the ligand in the PDBs used in this study. (FIXME! Add reasoning... or qualifier statement n=2) -->

## All CA-CB-Fe Angles

Figures can be found in \@ref(figs-cabAll)

<!-- All residues have a broad range of angles in relation to HEM. -->

<!-- Most residues have a broad range of angles for HEC, with the exception of THR, which has a tight distribution around 100 degrees. This result only appears here and does not follow for the closest residues, and therefore may be due to a small sample size of THR residues. -->

<!-- SRM appears to have tight distributions of angles when considering all residues; the residues closest to SRM do not echo this. Although likely attributable to a small sample size, there appear several residues with specific angles: ALA around 50 degrees, GLN around 140-150 degrees, and SER around 50 degrees. -->

<!-- Verdoheme... (FIXME! Confer with JeanDi before we report more of these angles. Not sure I'm going about it in an informative way. Also add figure numbers.) -->

## CA-CB-Fe Angles of Closest Residues

Figures can be found in \@ref(figs-cabClosest)

Most notably, HIS is the only residue that appears near verdoheme.

## Limitations of the Study
Limited sample size

Limited experimental data to reference to verify

NO experimental data in this study to verify, all theoretical

Only one software package/few algorithms used to calculate all these properties. Others were evaluated but none are compared w.

Algorithms may introduce bias based on how they work e.g. all the bubbles

Arbitrary selection of parameters; some based on rule of thumb or visual evaluation but all or almost all arbitrary

Unknown if the qualities measured are truly the most critical for the heme binding. Some papers suggest other properties may also be important but cannot be calculated, at least right now, e.g. ionic bonding strength etc.

Visual examination itself to OK the parameters/algorithms can introduce bias