`r if(knitr:::is_latex_output()) '\\startappendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->


# Figures{#a-figures}
\minitoc
<!-- Figures begin here  -->

## AA Frequency {#figs-aaFreqOverlaid}
```{r HEM-AAfreqOverlaid,fig.cap="HEM: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

   # AA FReq ----
   rm(tmp5A,tmp7A,tmpBoth)
   head(HEM_aaFreqDf)
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_aaFreqDf",sep="")))))
                          #HEM_aaFreqDf)
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_aaFreqDf",sep="")))))
   tmp7A$ang = '7'
   tmp5A$ang = '5'
   head(tmp7A)
   tmp7A
   tmp7A %>%
      dplyr::rename(
         df5A.Residue = df7A.Residue
      ) -> tmp7A
   merge(tmp5A,tmp7A,by = 'df5A.Residue') -> tmpBoth
   #alternative: left_join(tmp5A,tmp7A,by='df5A.Residue')
   tmpBoth %>%
      dplyr::rename(
         Residue = df5A.Residue
      ) -> tmpBoth
   tmpBoth
   
   library(reshape) #ONLY LOAD THIS HERE. IF YOU LOAD EALIER,
   # ALL CASE OF RENAME() FROM DPLYR PACKAGE IN ALL SCRIPTS GETS FUCKED UP.
   # PUTTING IT HERE, ONLY BELOW THIS LIBRARY LOAD DO YOU NEED NEED TO SPECIFY DPLYR::XXX
   
   to_plot <- reshape::melt((data.frame(x=tmpBoth$Residue,`Distance_5A`=tmpBoth$df5A.Freq,`Distance_7A`=tmpBoth$df7A.Freq)),id="x")
#   detach("package:reshape", unload=TRUE) #maybe avoid the problem anyway lol
   
   print(ggplot(to_plot,aes(x= reorder(x,-value),y=value,fill=variable)) + 
            geom_bar(stat="identity",position = "identity", alpha=.4) +
            labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency",sep='')) +
            scale_fill_discrete(name = "Distance Cutoff")+
            theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))
   
```

```{r HEC-AAfreqOverlaid,fig.cap="HEC: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

   # AA FReq ----
   rm(tmp5A,tmp7A,tmpBoth)
   head(HEM_aaFreqDf)
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_aaFreqDf",sep="")))))
                          #HEM_aaFreqDf)
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_aaFreqDf",sep="")))))
   tmp7A$ang = '7'
   tmp5A$ang = '5'
   head(tmp7A)
   tmp7A
   tmp7A %>%
      dplyr::rename(
         df5A.Residue = df7A.Residue
      ) -> tmp7A
   merge(tmp5A,tmp7A,by = 'df5A.Residue') -> tmpBoth
   #alternative: left_join(tmp5A,tmp7A,by='df5A.Residue')
   tmpBoth %>%
      dplyr::rename(
         Residue = df5A.Residue
      ) -> tmpBoth
   tmpBoth
   
   library(reshape) #ONLY LOAD THIS HERE. IF YOU LOAD EALIER,
   # ALL CASE OF RENAME() FROM DPLYR PACKAGE IN ALL SCRIPTS GETS FUCKED UP.
   # PUTTING IT HERE, ONLY BELOW THIS LIBRARY LOAD DO YOU NEED NEED TO SPECIFY DPLYR::XXX
   
   to_plot <- reshape::melt((data.frame(x=tmpBoth$Residue,`Distance_5A`=tmpBoth$df5A.Freq,`Distance_7A`=tmpBoth$df7A.Freq)),id="x")
#   detach("package:reshape", unload=TRUE) #maybe avoid the problem anyway lol
   
   print(ggplot(to_plot,aes(x= reorder(x,-value),y=value,fill=variable)) + 
            geom_bar(stat="identity",position = "identity", alpha=.4) +
            labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency",sep='')) +
            scale_fill_discrete(name = "Distance Cutoff")+
            theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))
   
```

```{r SRM-AAfreqOverlaid,fig.cap="SRM: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

   # AA FReq ----
   rm(tmp5A,tmp7A,tmpBoth)
   head(HEM_aaFreqDf)
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_aaFreqDf",sep="")))))
                          #HEM_aaFreqDf)
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_aaFreqDf",sep="")))))
   tmp7A$ang = '7'
   tmp5A$ang = '5'
   head(tmp7A)
   tmp7A
   tmp7A %>%
      dplyr::rename(
         df5A.Residue = df7A.Residue
      ) -> tmp7A
   merge(tmp5A,tmp7A,by = 'df5A.Residue') -> tmpBoth
   #alternative: left_join(tmp5A,tmp7A,by='df5A.Residue')
   tmpBoth %>%
      dplyr::rename(
         Residue = df5A.Residue
      ) -> tmpBoth
   tmpBoth
   
   library(reshape) #ONLY LOAD THIS HERE. IF YOU LOAD EALIER,
   # ALL CASE OF RENAME() FROM DPLYR PACKAGE IN ALL SCRIPTS GETS FUCKED UP.
   # PUTTING IT HERE, ONLY BELOW THIS LIBRARY LOAD DO YOU NEED NEED TO SPECIFY DPLYR::XXX
   
   to_plot <- reshape::melt((data.frame(x=tmpBoth$Residue,`Distance_5A`=tmpBoth$df5A.Freq,`Distance_7A`=tmpBoth$df7A.Freq)),id="x")
#   detach("package:reshape", unload=TRUE) #maybe avoid the problem anyway lol
   
   print(ggplot(to_plot,aes(x= reorder(x,-value),y=value,fill=variable)) + 
            geom_bar(stat="identity",position = "identity", alpha=.4) +
            labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency",sep='')) +
            scale_fill_discrete(name = "Distance Cutoff")+
            theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))
   
```

```{r VERDOHEME-AAfreqOverlaid,fig.cap="VERDOHEME: AA Frequency",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

   # AA FReq ----
   rm(tmp5A,tmp7A,tmpBoth)
   head(HEM_aaFreqDf)
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_aaFreqDf",sep="")))))
                          #HEM_aaFreqDf)
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_aaFreqDf",sep="")))))
   tmp7A$ang = '7'
   tmp5A$ang = '5'
   head(tmp7A)
   tmp7A
   tmp7A %>%
      dplyr::rename(
         df5A.Residue = df7A.Residue
      ) -> tmp7A
   merge(tmp5A,tmp7A,by = 'df5A.Residue') -> tmpBoth
   #alternative: left_join(tmp5A,tmp7A,by='df5A.Residue')
   tmpBoth %>%
      dplyr::rename(
         Residue = df5A.Residue
      ) -> tmpBoth
   tmpBoth
   
   library(reshape) #ONLY LOAD THIS HERE. IF YOU LOAD EALIER,
   # ALL CASE OF RENAME() FROM DPLYR PACKAGE IN ALL SCRIPTS GETS FUCKED UP.
   # PUTTING IT HERE, ONLY BELOW THIS LIBRARY LOAD DO YOU NEED NEED TO SPECIFY DPLYR::XXX
   
   to_plot <- reshape::melt((data.frame(x=tmpBoth$Residue,`Distance_5A`=tmpBoth$df5A.Freq,`Distance_7A`=tmpBoth$df7A.Freq)),id="x")
#   detach("package:reshape", unload=TRUE) #maybe avoid the problem anyway lol
   
   print(ggplot(to_plot,aes(x= reorder(x,-value),y=value,fill=variable)) + 
            geom_bar(stat="identity",position = "identity", alpha=.4) +
            labs(x = "Residue",y="Frequency", title = paste(activeLigand,": AA Frequency",sep='')) +
            scale_fill_discrete(name = "Distance Cutoff")+
            theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))
   
```


## Volume{#figs-vol}


```{r HEM-Volume,fig.cap="HEM: Volume",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

#    # ### VOLUME ####
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = 'volume_data'
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Volume (A³)",y="Frequency",title = paste(activeLigand,": Volume (A³)"))
   )
    
```

```{r HEC-Volume,fig.cap="HEC: Volume",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

#    # ### VOLUME ####
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = 'volume_data'
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Volume (A³)",y="Frequency",title = paste(activeLigand,": Volume (A³)"))
   )
    
```

```{r SRM-Volume,fig.cap="SRM: Volume",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

#    # ### VOLUME ####
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = 'volume_data'
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Volume (A³)",y="Frequency",title = paste(activeLigand,": Volume (A³)"))
   )
    
```

```{r VERDOHEME-Volume,fig.cap="VERDOHEME: Volume",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

#    # ### VOLUME ####
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = 'volume_data'
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Volume (A³)",y="Frequency",title = paste(activeLigand,": Volume (A³)"))
   )
    
```

## Ligand Excluded Surface Area{#figs-ligExcSA}

```{r HEM-Ligand-ExcludedSA,fig.cap="HEM: Ligand Excluded Suface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # Ligand Excluded Surface Area
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Excluded_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Excluded SA (A²)"))
   )
```

```{r HEC-Ligand-ExcludedSA,fig.cap="HEC: Ligand Excluded Suface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # Ligand Excluded Surface Area
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Excluded_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Excluded SA (A²)"))
   )
```

```{r SRM-Ligand-ExcludedSA,fig.cap="SRM: Ligand Excluded Suface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # Ligand Excluded Surface Area
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Excluded_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Excluded SA (A²)"))
   )
```

```{r VERDOHEME-Ligand-ExcludedSA,fig.cap="VERDOHEME: Ligand Excluded Suface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # Ligand Excluded Surface Area
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Excluded_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Excluded SA (A²)"))
   )
```


## Ligand Accessible Surface Area{#figs-ligAccSA}

```{r HEM-Ligand-AccessibleSA,fig.cap="HEM: Ligand Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Ligand Accessible Surface Area
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Accessible_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Accessible SA (A²)"))
   )
```

```{r HEC-Ligand-AccessibleSA,fig.cap="HEC: Ligand Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Ligand Accessible Surface Area
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Accessible_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Accessible SA (A²)"))
   )
```

```{r SRM-Ligand-AccessibleSA,fig.cap="SRM: Ligand Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Ligand Accessible Surface Area
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Accessible_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Accessible SA (A²)"))
   )
```

```{r VERDOHEME-Ligand-AccessibleSA,fig.cap="VERDOHEME: Ligand Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Ligand Accessible Surface Area
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = paste(activeLigand,"_Accessible_SA",sep="")
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area (A²)",y="Frequency",title = paste(activeLigand,": Ligand Accessible SA (A²)"))
   )
```


## Pocket Excluded Surface Area{#figs-pocketExcSA}

```{r HEM-Pocket-ExcludedSA,fig.cap="HEM: Pocket Excluded Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Excluded SA
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Excluded_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area A²",y="Frequency",title = paste(activeLigand,": Pocket Excluded SA (A²)"))
   )
```

```{r HEC-Pocket-ExcludedSA,fig.cap="HEC: Pocket Excluded Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Excluded SA
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Excluded_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area A²",y="Frequency",title = paste(activeLigand,": Pocket Excluded SA (A²)"))
   )
```

```{r SRM-Pocket-ExcludedSA,fig.cap="SRM: Pocket Excluded Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Excluded SA
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Excluded_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area A²",y="Frequency",title = paste(activeLigand,": Pocket Excluded SA (A²)"))
   )
```

```{r VERDOHEME-Pocket-ExcludedSA,fig.cap="VERDOHEME: Pocket Excluded Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Excluded SA
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)

   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Excluded_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(x="Surface Area A²",y="Frequency",title = paste(activeLigand,": Pocket Excluded SA (A²)"))
   )
```


## Pocket Accessible Surface Area{#figs-pocketAccSA}

```{r HEM-Pocket-AccessibleSA,fig.cap="HEM: Pocket Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Acessible histo
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Accessible_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(title = paste(activeLigand,"Pocket Acessible SA (A²)"))
   )
```

```{r HEC-Pocket-AccessibleSA,fig.cap="HEC: Pocket Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Acessible histo
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Accessible_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(title = paste(activeLigand,"Pocket Acessible SA (A²)"))
   )
```

```{r SRM-Pocket-AccessibleSA,fig.cap="SRM: Pocket Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Acessible histo
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Accessible_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(title = paste(activeLigand,"Pocket Acessible SA (A²)"))
   )
```

```{r VERDOHEME-Pocket-AccessibleSA,fig.cap="VERDOHEME: Pocket Accessible Surface Area",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # Pocket Acessible histo
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   rm(tmp5A,tmp7A,tmpBoth)
   colName = "Pocket_Accessible_SA"
   tmp7A <- data.frame(df7A = eval(parse(text=(paste(activeLigand,"_MERGED_DF$",colName,sep="")))))
   tmp5A <- data.frame(df5A = eval(parse(text=(paste("ls5A$",activeLigand,"_5A_MERGED_DF$",colName,sep="")))))
   tmp7A$Distance_Cutoff = '7A'
   tmp5A$Distance_Cutoff = '5A'
   tmp7A %>%
      dplyr::rename(
         df5A = df7A #hopefuly does not append, rm() should take care of that
      ) -> tmp7A
   tmpBoth <- rbind(tmp5A,tmp7A)
   print(
      ggplot(tmpBoth, aes(x=df5A,fill=Distance_Cutoff,color=)) +
         geom_histogram(position="identity",alpha=0.4)
      + labs(title = paste(activeLigand,"Pocket Acessible SA (A²)"))
   )
```


## All Planar Angles{#figs-planarAll}

```{r HEM-planarAll,fig.cap="HEM: All Planar Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all planar angles
   # yeah keep the as.numeric(as.character),easiest way to solve the problem
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)



   planarAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All Planar Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarAllPlot)
```

```{r HEC-planarAll,fig.cap="HEC: All Planar Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all planar angles
   # yeah keep the as.numeric(as.character),easiest way to solve the problem
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)



   planarAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All Planar Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarAllPlot)
```

```{r SRM-planarAll,fig.cap="SRM: All Planar Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all planar angles
   # yeah keep the as.numeric(as.character),easiest way to solve the problem
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)



   planarAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All Planar Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarAllPlot)
```

```{r VERDOHEME-planarAll,fig.cap="VERDOHEME: All Planar Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all planar angles
   # yeah keep the as.numeric(as.character),easiest way to solve the problem
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)



   planarAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All Planar Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarAllPlot)
```

## Planar Angles of Closest Residues{#figs-planarClosest}

```{r HEM-planarClosest,fig.cap="HEM: Planar Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # closest residues' planar angles
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   planarMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim = FALSE) +
      labs(title = paste(activeLigand,": Planar Angles of Closest Residues",sep = ''),x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarMinPlot)
 
```

```{r HEC-planarClosest,fig.cap="HEC: Planar Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # closest residues' planar angles
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   planarMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim = FALSE) +
      labs(title = paste(activeLigand,": Planar Angles of Closest Residues",sep = ''),x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarMinPlot)
 
```

```{r SRM-planarClosest,fig.cap="SRM: Planar Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # closest residues' planar angles
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   planarMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim = FALSE) +
      labs(title = paste(activeLigand,": Planar Angles of Closest Residues",sep = ''),x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarMinPlot)
 
```

```{r VERDOHEME-planarClosest,fig.cap="VERDOHEME: Planar Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}
   # closest residues' planar angles
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   planarMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistPlanarDf",sep=''))),
                           aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim = FALSE) +
      labs(title = paste(activeLigand,": Planar Angles of Closest Residues",sep = ''),x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(planarMinPlot)
 
```

## All CA-CB-Fe Angles {#figs-cabAll}

```{r HEM-cab-All,fig.cap="HEM: All CA-CB-Fe Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all cabs with distance intersect
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All CA-CB-Fe Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabAllPlot)
   
```

```{r HEC-cab-All,fig.cap="HEC: All CA-CB-Fe Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all cabs with distance intersect
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All CA-CB-Fe Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabAllPlot)
   
```

```{r SRM-cab-All,fig.cap="SRM: All CA-CB-Fe Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all cabs with distance intersect
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All CA-CB-Fe Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabAllPlot)
   
```

```{r VERDOHEME-cab-All,fig.cap="VERDOHEME: All CA-CB-Fe Angles",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # all cabs with distance intersect
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabAllPlot <- ggplot(eval(parse(text=paste(activeLigand,"_allDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": All CA-CB-Fe Angles",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabAllPlot)
   
```

## CA-CB-Fe Angles of Closest Residues{#figs-cabClosest}

```{r HEM-cabClosest,fig.cap="HEM: CACBFe Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # cabs for closest 3 residues
load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": CA-CB-Fe Angles of Closest Residues",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabMinPlot)

```


```{r HEC-cabClosest,fig.cap="HEC: CACBFe Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # cabs for closest 3 residues
load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": CA-CB-Fe Angles of Closest Residues",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabMinPlot)

```


```{r SRM-cabClosest,fig.cap="SRM: CACBFe Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # cabs for closest 3 residues
load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": CA-CB-Fe Angles of Closest Residues",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabMinPlot)

```


```{r VERDOHEME-cabClosest,fig.cap="VERDOHEME: CACBFe Angles of Closest Residues",echo=FALSE, message= FALSE, warning=FALSE, results=FALSE}

   # cabs for closest 3 residues
load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra)


   cabMinPlot <- ggplot(eval(parse(text=paste(activeLigand,"_minDistCabDf",sep=''))),
                        aes(x=Residue_Code.x,y=as.numeric(as.character(Angle)),fill=Residue_Code.x)) +
      geom_violin(trim=FALSE) +
      labs(title = paste(activeLigand,": CA-CB-Fe Angles of Closest Residues",sep=''), x="Residue",y="Angle") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
   print(cabMinPlot)

```



# Tables{#a-tables}
\minitoc
<!-- Tables begin here  -->


## Molecule Names and Source Organisms{#molOrgSec}
```{r HEM-molOrg,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 
#source("~/heme-binding/scripts/r/data5A.R") 
#ls5A <- data5A_fn()


HEM_p1DF %>%
  kable(longtable = T, booktabs = T, caption = "HEM: Molecules and Source Organisms") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
```

```{r HEC-molOrg,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 
#source("~/heme-binding/scripts/r/data5A.R") 
#ls5A <- data5A_fn()


HEC_p1DF %>%
  kable(longtable = T, booktabs = T, caption = "HEC: Molecules and Source Organisms") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
```

```{r SRM-molOrg,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 
#source("~/heme-binding/scripts/r/data5A.R") 
#ls5A <- data5A_fn()


SRM_p1DF %>%
  kable(longtable = T, booktabs = T, caption = "SRM: Molecules and Source Organisms") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
```

```{r VERDOHEME-molOrg,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 
#source("~/heme-binding/scripts/r/data5A.R") 
#ls5A <- data5A_fn()


VERDOHEME_p1DF %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: Molecules and Source Organisms") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
```

## Distances 

### All Distances from Heme Fe to Atoms of Residues in Binding Pocket 
```{r HEM-t-distancesAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_distList$all_distances %>%
  kable(longtable = T, booktabs = T, caption = "HEM: All Distances, Atoms to Fe") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

### Mean Distances of Each Residue in Binding Pocket

```{r HEM-t-distancesMean,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_distList$mean_distances %>%
  kable(longtable = T, booktabs = T, caption = "HEM: Mean Distances of Each Residue in Pocket") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```



## Volume and Surface Areas
```{r HEM-volSA,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_p2DF %>%
  kable(longtable = T, booktabs = T, caption = "HEM: Volume and Surface Areas") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r HEC-volSA,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_p2DF %>%
  kable(longtable = T, booktabs = T, caption = "HEC: Volume and Surface Areas") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r SRM-volSA,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_p2DF %>%
  kable(longtable = T, booktabs = T, caption = "SRM: Volume and Surface Areas") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r VERDOHEME-volSA,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_p2DF %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: Volume and Surface Areas") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

## All Planar Angles
```{r HEM-t-planarAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_allDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM: All Planar Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r HEC-t-planarAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_allDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC: All Planar Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r SRM-t-planarAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_allDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM: All Planar Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r VERDOHEME-t-planarAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_allDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: All Planar Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

## Planar Angles of Closest Residues
```{r HEM-t-planarClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_minDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM: Planar Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r HEC-t-planarClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_minDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC: Planar Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r SRM-t-planarClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_minDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM: Planar Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r VERDOHEME-t-planarClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_minDistPlanarDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: Planar Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

## All CA-CB-Fe Angles
```{r HEM-t-cabAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_allDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM: All CA-CB-Fe Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r HEC-t-cabAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_allDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC: All CA-CB-Fe Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r SRM-t-cabAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_allDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM: All CA-CB-Fe Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r VERDOHEME-t-cabAll,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_allDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: All CA-CB-Fe Angles") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

## CA-CB-Fe Angles of Closest Residues
```{r HEM-t-cabClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEM_minDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "HEM: CA-CB-Fe Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r HEC-t-cabClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "HEC"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

HEC_minDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "HEC: CA-CB-Fe Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r SRM-t-cabClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "SRM"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

SRM_minDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "SRM: CA-CB-Fe Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```

```{r VERDOHEME-t-cabClosest,echo=FALSE, message= FALSE, warning=FALSE}
# declarations

load("mainData.RData")
activeLigand = "VERDOHEME"
library(dplyr) 
library(data.table)
library(tidyr)
library(ggplot2) 
library(stringr)
library(knitr)
library(clipr) # Linux) sudo apt-get install xclip ... R)install.packages("clipr")  
source("~/heme-binding/scripts/r/addpdbcol.R")
library(kableExtra) 

VERDOHEME_minDistCabDf %>%
  kable(longtable = T, booktabs = T, caption = "VERDOHEME: CA-CB-Fe Angles of Closest Residues") %>%
   kable_styling(full_width = T, latex_options = c("striped","repeat_header")) %>%
                    row_spec(0,angle=45)
  
```


<!-- This is an attempt at referencing the tables above.  -->

<!-- <!-- These do work, but only when knitting from Index --> 
<!-- figure reference \@ref(fig:super-figs) -->
<!-- table reference \@ref(tab:HEM-p1DF) -->